Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-28 EMNLP-demo-paper/relatedWorks.tex
update intro
add figure

Visualizing and understanding neural models in nlp
Understanding Neural Networks through Representation Erasure

Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
\textcolor{blue}{Lee visualizes the beam search and attention component in the NMT model. The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.}

End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
\textcolor{blue}{Instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map. In this platform, user able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.}

>>>>

Visualizing and understanding neural models in nlp \cite{LiChenHovy2015}
Understanding Neural Networks through Representation Erasure \cite{li2016understanding}

AllenNLP demo

%Interactive Visualization and Manipulation of Attention-based Neural Machine Translation
Lee et al. visualizes the beam search and attention component in the NMT model~\cite{lee2017interactive}. The work allows user involve into the decision-making process by enabling dynamic change the probability for the next step of the search tree or change the weight value of the attention.
%}

%End-to-End Non-Factoid Question Answering with an Interactive Visualization of Neural Attention Weights
%\textcolor{blue}{
In the recent attention visualization work focus on question and answering model~\cite{ruckle2017end}, 
instead of visualizing the attention matrix directly, the system shows the text context and highlights the critical phrase, which used to answers the questions, using color map. In this system, the user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.
%}

### 2018-05-28 EMNLP-demo-paper/system.tex
update intro
add figure

\section{System}
We design the proposed system with modularity in mind
\subsection{Input Perturbation}

>>>>

\section{System}
We design the proposed system with modularity in mind

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{attentionPanels}
  \vspace{-6mm}
 \caption{
Attention visualization. In the graph attention view (a), a bipartite graph encoding is adopted, in which the edge thickness corresponds to the attention value. In the matrix attention view (b), the entries of $i^{th}$ row represent the probabilities of words in hypotheses align to the $i^{th}$ word in the premise.
The user can alter the attention values via the pop-up interface illustrated in (c).
We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentence based on the dependency tree.
%
For highly asymmetric attention relationship, we utilized a zoomable hierarchical visual representation (d).
}
\label{fig:pipelineUpdate}
\end{figure*}

\subsection{Attention Views}
Bipartie graph
Attention matrix

\subsection{Perturbation based exploration}
\label{sec:perturb}

\subsection{Prediction Summarization}
